The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-01-26 paper/paper.tex
extra sentence

>>>>

An iterative precedure was used to progressively change the target bin edges to optimize one of the metrics (FOMs or SNRs) between the trainings of the classifiers. In general, we recover different choices for each statistic, but the differences are relatively marginal. This procedure was done by hand for this challenge, but could be automated and applied to any kind of classifier.
